Bioverse: The Habitable Zone Inner Edge Discontinuity as an Imprint of Runaway Greenhouse Climates on Exoplanet Demographics

### 2023-08-16 src/tex/ms.tex
add DOI of archived repo on Zenodo

%\section*{Data Availability}
\section*{Reproducibility}
%All data sets and software required to reproduce our results and this article are available through GitHub and Zenodo.
This study uses the reproducibility framework ``showyourwork''~\citep{Luger2021}.
All code required to reproduce our results, figures, and this article itself is available at \url{https://github.com/matiscke/hz-inner-edge-discontinuity}.
The code to reproduce a figure can be accessed via the icon link next to the respective figure caption.
\rev{Data sets associated with this work are available at \dataset[doi:10.5281/zenodo.7080391]{\doi{10.5281/zenodo.7080391}}~(stellar luminosity tracks from \citet{Baraffe1998}) and \dataset[doi:10.5281/zenodo.7946446]{\doi{10.5281/zenodo.7946446}} (results from model grid runs of \bioverse).}

>>>>

%\section*{Data Availability}
\section*{Reproducibility}
%All data sets and software required to reproduce our results and this article are available through GitHub and Zenodo.
This study uses the reproducibility framework ``showyourwork''~\citep{Luger2021}.
All code required to reproduce our results, figures, and this article itself is available at \url{https://github.com/matiscke/hz-inner-edge-discontinuity}\rev{, and the repository state at the time of paper acceptance can be found at \dataset[doi:10.5281/zenodo.8251077]{\doi{10.5281/zenodo.8251077}}}.
The code to reproduce a figure can be accessed via the icon link next to the respective figure caption.
\rev{Data sets associated with this work are available at \dataset[doi:10.5281/zenodo.7080391]{\doi{10.5281/zenodo.7080391}}~(stellar luminosity tracks from \citet{Baraffe1998}) and \dataset[doi:10.5281/zenodo.7946446]{\doi{10.5281/zenodo.7946446}} (results from model grid runs of \bioverse).}
